---
title: "B_merge"
---

# LEALCO-BEH

# Information

### Goal

Analyse data *from test task*

### Inputs

The output file is a large .csv table containing the entire data of the file in a long format. It puts together the PsychoPy input files, the demographics, the VOT files as well as the relevant information from the debriefing questionnaire.

# Load packages

```{r}
library(dplyr)
library(tidyverse)
library(lme4)
library(buildmer)
library(emmeans)
library(lmerTest)
library(gridExtra)
library(sjPlot)
source("R/utils.R")
```

# Set some custom settings

```{r}
theme_set(theme_bw())
pal1 = c("#F5793A", "#4f5dab")
```

# Read files

Read files

```{r}
data <- read.csv('data/LEALCO-BEH_test_merged_data.csv')
demo <- read.csv('data/demographic/LEALCO-BEH_demographics.csv',  sep = ";", fileEncoding = "Latin1", check.names = F)
```

Clean-up variables and variables names.

```{r}

data$subjID <- as_factor(data$subjID)
data$partner_order <- as_factor(data$partner_order)
data$key_trained <- as_factor(data$key_trained)
data$key_untrained <- as_factor(data$key_untrained)
data$block <- as_factor(data$block)
data$partner <- as_factor(data$partner)
data$class <- as_factor(data$class)
data$partner_type <- as_factor(data$partner_type)
data$SUBTLEX_frequency_log_cat <- as_factor(data$SUBTLEX_frequency_log_cat)
data$error <- as_factor(data$error)
data$target_label <- as_factor(data$target_label)
data$Geschlecht <- as_factor(data$Geschlecht)
data$Händigkeit <- as_factor(data$Händigkeit)
data$VOT <- as.numeric(data$VOT)
data$correct <- as.numeric(data$correct)
demo$Alter <- as.numeric(demo$Alter )
```

# Preliminary data sanity checks

## (1) Check general error pattern

Here, the general error distribution (regardless of experimental condition) is assessed by subject. This can potentially constitute the basis for data exclusion.

| Code    | Meaning                                     |
|---------|---------------------------------------------|
| correct | said exactly what they were expected to say |
| 1       | compounded                                  |
| 2       | semantically related                        |
| 3       | phonologically related                      |
| 4       | unrelated                                   |
| 5       | misarticulation                             |
| 6       | other                                       |
| 7       | visual                                      |
| 8       | audio recording error                       |
| 9       | no response                                 |

: Table 1: Key for interpreting the "Error"" variable

```{r}
# plot accuracy counts by subject
pdf("output_figures/LEALCO-BEH_raw screening.pdf")
p <- ggplot(data, aes(x=error, fill=error)) + 
  geom_bar() +
  facet_wrap(~subjID)
p
dev.off()
p

# count how many trials of each type
data %>% count(error) 

```

## (2) Check general RT pattern

Let's screen for anomalous RTs in the data files, which could have originated from inaccuracies in data reprocessing. It appears that no anomalies are (any longer) present in the data.

```{r}

# overall density plot
plot(density(data$VOT, na.rm = TRUE))

# zooming into the left part of the histogramm to spot anomalous VOTs (<400 ms), and export them.
hist(data$VOT, xlim=c(0, 1000), breaks = 1000)
dummy <- data[data$VOT < 400,]
write.csv(dummy, 'data/LEALCO-BEH_test_anomalous_RTs.csv', row.names=FALSE, fileEncoding = "UTF-8")

# Look for NA values and export them.
dummy <- data[is.na(data$VOT),]
write.csv(dummy, 'data/LEALCO-BEH_test_anomalousNA_RTs.csv', row.names=FALSE, fileEncoding = "UTF-8")

# histogramm fo ronly correct responses
hist(data$VOT[data$correct == 1], xlim=c(0, 1000), breaks = 1000)
plot(density(data$VOT[data$correct == 1], na.rm = TRUE))
```

## (3) Transform non-normal variables

After trying several normalization approaches, it appears that the **inverse** **normalization** is most appropriatel.

```{r}

# plot native VOTs
hist(data$VOT, breaks=500)

# plot log10 notmalized VOTs
data$VOTlog10 <- log10(data$VOT)
hist(data$VOTlog10, breaks=500)

# plot inverse normalized VOTs
data$VOTinv <- 1/data$VOT
hist(data$VOTinv, breaks=500)

# plot square root normalized VOTs
data$VOTsqrt <- sqrt(data$VOT)
hist(data$VOTsqrt, breaks=500)
```

## (4) Are there anomalous subjects?

Calculate descriptive across collapsed conditions. Note that no trials/subjects are excluded.

```{r}

# descritpives of accuracy: within-subjects
summary_acc_wSubj <- data %>%
  group_by(subjID) %>%
  summarise(mean_ACC = mean(correct), sd=sd(correct), sem=(sd(correct)/sqrt((length(correct)))))

# descritpives of accuracy: between-subjects
summary_acc_bSubj <- summary_acc_wSubj %>%
  summarise(grand_mean_ACC = mean(mean_ACC), sd=sd(mean_ACC), sem=(sd(mean_ACC)/sqrt((length(mean_ACC)))))

# descritpives of vot: within-subjects
summary_vot_wSubj <- data %>%
  filter(correct == 1) %>%
  group_by(subjID) %>%
  summarise(mean_VOT = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))))

# descritpives of vot: between-subjects
summary_vot_bSubj <- summary_vot_wSubj %>%
  summarise(grand_mean_VOT = mean(mean_VOT), sd=sd(mean_VOT), sem=(sd(mean_VOT)/sqrt((length(mean_VOT)))))
```

# Subject exclusion

Select trained trials, with a focus on those that are valid, i.e. where no recording error occurred. We therefore exclude all trials coded as: (5) misarticulation, (6) other, (7) visual, (8) audio recording error (9) no response.

```{r}
data_trained <- data %>%
  filter(class == 'test item') %>%
  filter(error %in% c('correct', '1', '2', '3', '4'))
```

Determine if any subjects need to be excluded based on data distribution for **accuracy** (collapsing all test conditions).

```{r}

# aggregate within subject
data_trained_sum_wSubj <- data_trained %>%
  group_by(subjID) %>%
  summarise(mean = mean(correct), sem=(sd(correct)/sqrt((length(correct)))), sd=sd(correct))

# aggregate between subjects
data_trained_sum_bSubj <- data_trained_sum_wSubj %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_trained_sum_bSubj$grandMean + data_trained_sum_bSubj$sd * 2
minus2SD = data_trained_sum_bSubj$grandMean - data_trained_sum_bSubj$sd * 2
plus25SD = data_trained_sum_bSubj$grandMean + data_trained_sum_bSubj$sd * 2.5
minus25SD = data_trained_sum_bSubj$grandMean - data_trained_sum_bSubj$sd * 2.5
plus3SD = data_trained_sum_bSubj$grandMean + data_trained_sum_bSubj$sd * 3
minus3SD = data_trained_sum_bSubj$grandMean - data_trained_sum_bSubj$sd * 3

# plot
pdf("output_figures/LEALCO-BEH_acc_outliers.pdf")
ggplot(data_trained_sum_wSubj, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_trained_sum_bSubj$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_trained_sum_bSubj$grandMean, y=3, label="mean", angle = 30) +
  xlim(0,1) +
 ggtitle("Subject outliers based on accuracy")
dev.off()

# select outliers on the basis of +/-2.5 SD
data_trained_sum_wSubj[data_trained_sum_wSubj$mean < minus25SD |
                       data_trained_sum_wSubj$mean > plus25SD, ]
```

Do same thing with **naming latencies**.

```{r}

# aggregate within subject
data_trained_sum_wSubj_vot <- data_trained %>%
  group_by(subjID) %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), sd=sd(VOT))

# aggregate between subjects
data_trained_sum_bSubj_vot <- data_trained_sum_wSubj_vot %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_trained_sum_bSubj_vot$grandMean + data_trained_sum_bSubj_vot$sd * 2
minus2SD = data_trained_sum_bSubj_vot$grandMean - data_trained_sum_bSubj_vot$sd * 2
plus25SD = data_trained_sum_bSubj_vot$grandMean + data_trained_sum_bSubj_vot$sd * 2.5
minus25SD = data_trained_sum_bSubj_vot$grandMean - data_trained_sum_bSubj_vot$sd * 2.5
plus3SD = data_trained_sum_bSubj_vot$grandMean + data_trained_sum_bSubj_vot$sd * 3
minus3SD = data_trained_sum_bSubj_vot$grandMean - data_trained_sum_bSubj_vot$sd * 3

# plot
pdf("output_figures/LEALCO-BEH_vot_outliers.pdf")
ggplot(data_trained_sum_wSubj_vot, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_trained_sum_bSubj_vot$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_trained_sum_bSubj_vot$grandMean, y=3, label="mean", angle = 30) +
  xlim(0,NA) 
  ggtitle("Subject outliers based on naming latency (native)")
dev.off()

# select outliers on the basis of +/-2.5 SD
data_trained_sum_wSubj_vot[data_trained_sum_wSubj_vot$mean < minus25SD |
                       data_trained_sum_wSubj_vot$mean > plus25SD, ]
```

Do the same with **inverted naming latencies**.

```{r}

# aggregate within subject
data_trained_sum_wSubj_votINV <- data_trained %>%
  group_by(subjID) %>%
  summarise(mean = mean(VOTinv), sem=(sd(VOTinv)/sqrt((length(VOTinv)))), sd=sd(VOTinv))

# aggregate between subjects
data_trained_sum_bSubj_votINV <- data_trained_sum_wSubj_votINV %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_trained_sum_bSubj_votINV$grandMean + data_trained_sum_bSubj_votINV$sd * 2
minus2SD = data_trained_sum_bSubj_votINV$grandMean - data_trained_sum_bSubj_votINV$sd * 2
plus25SD = data_trained_sum_bSubj_votINV$grandMean + data_trained_sum_bSubj_votINV$sd * 2.5
minus25SD = data_trained_sum_bSubj_votINV$grandMean - data_trained_sum_bSubj_votINV$sd * 2.5
plus3SD = data_trained_sum_bSubj_votINV$grandMean + data_trained_sum_bSubj_votINV$sd * 3
minus3SD = data_trained_sum_bSubj_votINV$grandMean - data_trained_sum_bSubj_votINV$sd * 3

# plot
pdf("output_figures/LEALCO-BEH_votINV_outliers.pdf")
ggplot(data_trained_sum_wSubj_votINV, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_trained_sum_bSubj_votINV$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_trained_sum_bSubj_votINV$grandMean, y=3, label="mean", angle = 30) +
  ggtitle("Subject outliers based on naming latency (inverted)")
dev.off()

# select outliers on the basis of +/-2.5 SD
data_trained_sum_wSubj_votINV[data_trained_sum_wSubj_votINV$mean < minus25SD |
                       data_trained_sum_wSubj_votINV$mean > plus25SD, ]
```

Overall, this condition-blind analysis of outliers showed that, for the **accuracy** measure, applying the following threshold results in excluding following subjects:

-   **2 SD:** 15, 25

-   **2.5 SD:** 15

-   **3 SD:** 15

For the **(native)** **VOT** measure applying the following threshold results in excluding following subjects:

-   **2 SD:** 15

-   **2.5 SD:** 15

-   **3 SD:** 15

For the **(inverted)** **VOT** measure applying the following threshold results in excluding following subjects:

-   **2 SD:** 15

-   **2.5 SD:** 15

-   **3 SD:** 15

In addition, subject 20 reported not having a "normal or corrected-to-normal" hearing and has therefore been excluded from the analyses.

We select the exclusion criteria of +/-3SD resulting in the exclusion of subjects 15 and 20.

```{r}
exclusion_acc <- c('15', '22', '27', '28')
exclusion_vot <- c('15', '22', '27', '28')
```

# Trial Overview

Here, we generate some summary statistic about trial classification (after remoing outliers).

```{r}

# select data (only on test items, but before filtering for invalid trials)
data_overview <- data %>%
  filter(class == 'test item') 
data_overview$error <- as_factor(data_overview$error)

# aggregte (within subject)
overview_wSubj <- data_overview %>%
  filter(!subjID %in% exclusion_acc) %>%
  group_by(subjID, error) %>%
  summarise(n = n()) %>%
  complete(error, fill = list(n = 0)) %>%
  group_by(subjID) %>%
  mutate(
    perc = n / sum(n) * 100
  ) %>%
  ungroup()

# aggregte (between subject)
overview_bSubj <- overview_wSubj %>%
  group_by(error) %>%
  summarise(count_mean = mean(n), count_sd = sd(n), perc_mean = mean(perc), perc_sd = sd(perc))

# save
write.csv(overview_bSubj, "output_stats/LEALCO-BEH_trial_overview.csv")
```

# Sample statistics

```{r}

# sample ACC
sample_ACC <- demo %>%
  filter(!subjID  %in%  exclusion_acc) %>%
  summarise(age_mean = mean(Alter, na.rm = TRUE), age_sd=sd(Alter, na.rm = TRUE),
            n=length(subjID))
sample_ACC_sex <- demo %>%
  filter(!subjID  %in%  exclusion_acc) %>%
  group_by(Geschlecht) %>%
  summarize(n= n()) %>%
  pivot_wider(names_from=Geschlecht, values_from=n)
sample_ACC <- cbind(sample_ACC, sample_ACC_sex)

# sample VOTinv
sample_VOTinv <- demo %>%
  filter(!subjID  %in%  exclusion_vot) %>%
  summarise(age_mean = mean(Alter, na.rm = TRUE), age_sd=sd(Alter, na.rm = TRUE),
            n=length(subjID))
sample_VOTinv_sex <- demo %>%
  filter(!subjID  %in%  exclusion_vot) %>%
  group_by(Geschlecht) %>%
  summarize(n= n()) %>%
  pivot_wider(names_from=Geschlecht, values_from=n)
sample_VOTinv <- cbind(sample_VOTinv, sample_VOTinv_sex)

# save
write.csv(sample_ACC, "output_stats/LEALCO-BEH_demographic_summary_ACCsample.csv")
write.csv(sample_VOTinv, "output_stats/LEALCO-BEH_demographic_summary_VOTinvsample.csv")
```

# == Label Maintenance ==

## Descriptive analysis

### By Subject (partner)

Here we just have a simple look at accuracy, that is we consider correct only those trials where the subject said *exactly* the word they were expected to say.

```{r}

# aggregte (within subject)
acc_wSubj_partner <- data_trained %>%
  filter(!subjID %in%  exclusion_acc) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean = mean(correct), sd=sd(correct), sem=(sd(correct)/sqrt((length(correct)))), n=length(correct))

# save
write.csv(acc_wSubj_partner, "output_stats/LEALCO-BEH_accuracy_withinSubjects_partner.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH_accuracy_withinSubjects_partner_barplot.pdf")
a <- ggplot(acc_wSubj_partner, aes(y=mean, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
    scale_fill_manual(values = pal1) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off() 
a
```

```{r}
# aggregte (between subject)
acc_bSubj_partner <- acc_wSubj_partner %>%
  group_by(partner_type) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(acc_bSubj_partner, "output_stats/LEALCO-BEH_accuracy_betweenSubjects_partner.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH_accuracy_betweenSubjects_partner_barplot.pdf")
c <- ggplot(acc_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = pal1) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1)
c
dev.off()
c

# make other more transparent plot
pdf("output_figures/LEALCO-BEH_accuracy_betweenSubjects_partner_pointplot.pdf")
zz <- ggplot(acc_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_point(data= acc_wSubj_partner, aes(y=mean, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=3) + 
  scale_colour_manual(values = pal1) +
    geom_point(stat="identity", color = "black", position=position_dodge(), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1)
zz
dev.off()
zz
```

### By Subject (partner x block)

Now we do the same procedure, but while also accounting for block

```{r}
# aggregte (within subject)
acc_wSubj_partner_block <- data_trained %>%
  filter(!subjID %in%  exclusion_acc) %>%
  group_by(subjID, partner_type, block) %>%
  summarise(mean = mean(correct), sd=sd(correct), sem=(sd(correct)/sqrt((length(correct)))), n=length(correct))

# save
write.csv(acc_wSubj_partner_block, "output_stats/LEALCO-BEH_accuracy_withinSubjects_partner_x_block.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH_accuracy_withinSubjects_partner_x_block_barplot.pdf")
a <- ggplot(acc_wSubj_partner_block, aes(y=mean, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}
# aggregte (between subject)
acc_bSubj_partner_block <- acc_wSubj_partner_block %>%
  group_by(partner_type,block) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(acc_bSubj_partner_block, "output_stats/LEALCO-BEH_accuracy_betweenSubjects_partner_x_block.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-BEH_accuracy_betweenSubjects_partner_x_block_barplot.pdf")
c <- ggplot(acc_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1)
c
dev.off()
c

# more trasparent plot
pdf("output_figures/LEALCO-BEH_accuracy_betweenSubjects_partner_x_block_pointplot.pdf")
tt <- ggplot(acc_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_point(data= acc_wSubj_partner_block, aes(y=mean, x=block, color=partner_type), stat="identity", position = position_jitterdodge(jitter.w = 0.05, dodge.width=(.9)), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### By Items (partner)

```{r}

# aggregte (within item)
acc_wItem_partner <- data_trained %>%
  group_by(target_label, partner_type) %>%
    summarise(mean = mean(correct), sd=sd(correct), sem=(sd(correct)/sqrt((length(correct)))), n=length(correct))

# save
write.csv(acc_wItem_partner, "output_stats/LEALCO-BEH_accuracy_withinItems_partner.csv", row.names = FALSE)

# plot (within item)
pdf("output_figures/LEALCO-BEH_accuracy_withinItems_partner_barplot.pdf")
a <- ggplot(acc_wItem_partner, aes(y=mean, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~target_label)
a
dev.off()
a
```

## LMM

Prepare the ACC data for LMMs.

```{r}
# for each trial, cretae new variable containing the perceived quality of teamwork, dependin gon the current partner (this just takes the correct value from the debfirefing questionnaire, depending on which partner the trial took place with)
data_trained$team  <- ifelse(data_trained$partner == 'A', data_trained$T101, data_trained$T201)

# select data
acc <- data_trained %>%
  filter(!subjID %in%  exclusion_acc)

# Set sum contrasts for all variables.
acc$partner_type <- droplevels(acc$partner_type)
contrasts(acc$partner_type) <- contr.sum(2)
contrasts(acc$block)  <- contr.sum(2)

# check contrasts
contrasts(acc$partner_type)
contrasts(acc$block)

# center covariates
acc <- acc %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

acc <- acc %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

acc <- acc %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

acc <- acc %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

Try to find the maximally convergent model by using the *buildmer()* approach.

**/!\\ MIGHT TAKE \>1h TO RUN /!\\**

```{r}
# indicate the maximal effect srucutre (both fixend and rendom) that is motivated based on design & hypotheses
f <- correct ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# select the maximal model that still converges
m_acc <- buildmer(f,family=binomial, data=acc,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_acc)

sink("output_stats/LEALCO-BEH_acc_lmm.txt")
print(summary(m_acc))
sink()  # returns output to the console

save_model_to_html(m_acc@model, 3,  "LEALCO-BEH_acc_lmm.html")
```

Make usual sanity checks for the winning model.

```{r}
# qqplot
pdf("output_figures/LEALCO-BEH_acc_lmm_qqplot.pdf")
qqnorm(residuals(m_acc))
dev.off()

# histogram
pdf("output_figures/LEALCO-BEH_acc_lmm_hist.pdf")
hist(residuals(m_acc))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-BEH_acc_lmm_residuals.pdf")
plot(residuals(m_acc))
dev.off()
```

### Post-hoc / marginal means (Partner Type)

```{r}
# make post-hoc with no correction
m_acc.emm_none_partner <-emmeans(m_acc@model, pairwise ~ partner_type, adjust = "none")
m_acc.emm_none_partner.ph_none_partner <- as.data.frame(m_acc.emm_none_partner$contrasts)
write.csv(m_acc.emm_none_partner,"output_stats/LEALCO-BEH_acc_ph_none.csv", row.names = FALSE)

# extract and save marginal means
m_acc.mm_partner <- as.data.frame(m_acc.emm_none_partner$emmeans)
m_acc.mm_partner$emmean_untrans <- plogis(m_acc.mm_partner$emmean)
m_acc.mm_partner$asymp.LCL_untrans <- plogis(m_acc.mm_partner$asymp.LCL)
m_acc.mm_partner$asymp.UCL_untrans <- plogis(m_acc.mm_partner$asymp.UCL)

# save them
write.csv(m_acc.mm_partner,"output_stats/LEALCO-BEH_acc_lmm_marginalMeans_partner.csv", row.names = FALSE)

# visualize marginal means
tt <- ggplot(m_acc.mm_partner, aes(y=emmean_untrans*100, x=partner_type, color=partner_type)) + 
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans*100, ymax=asymp.UCL_untrans*100), width=.2, position=position_dodge(.9)) +
  labs(y="Label Maintenance (%)", x="Partner") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,100)
tt
ggsave("output_figures/LEALCO-BEH_acc_lmm_marginal_partner_pointplot.pdf", width=4
       , height=3.5)
tt
```

# == Naming Latencies (at correct trials) ==

## Descriptive statistics

### By Subject (native, partner)

Here we just have a simple look at naming latencies, while considering only trials that are correct. In a first moment, we just examine naming latencies in their native format, that is without any type of normalization for approximating normality. Note that the data is right-skewed, expected for latency data.

```{r}
# aggregte (within subject)
vot_wSubj_partner <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), n=length(VOT))

# save
write.csv(vot_wSubj_partner, "output_stats/LEALCO-BEH_vot_withinSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-BEH_vot_withinSubjects_partner_barplot.pdf")
a <- ggplot(vot_wSubj_partner, aes(y=mean, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=16)) +
  #ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}

# aggregate (between subject)
vot_bSubj_partner <- vot_wSubj_partner %>%
  group_by(partner_type) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(vot_bSubj_partner, "output_stats/LEALCO-BEH_vot_betweenSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-BEH_vot_betweenSubjects_partner_barplot.pdf")
c <- ggplot(vot_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16))
c
dev.off()
c

# plot (raincloud)
pdf("output_figures/LEALCO-BEH_vot_betweenSubjects_partner_pointplot.pdf")
tt <- ggplot(vot_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_point(data= vot_wSubj_partner, aes(y=mean, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### By Subjects (native, partner x block)

Now we do the same procedure, but while also accounting for block.

```{r}
# aggregte (within subject)
vot_wSubj_partner_block <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, partner_type, block) %>%
    summarise(mean = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), n=length(VOT))

# save
write.csv(vot_wSubj_partner_block, "output_stats/LEALCO-BEH_vot_withinSubjects_partner_x_block.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-BEH_vot_withinSubjects_partner_x_block_barplot.pdf")
a <- ggplot(vot_wSubj_partner_block, aes(y=mean, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
      labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}

# aggregte (between subject)
vot_bSubj_partner_block <- vot_wSubj_partner_block %>%
  group_by(partner_type,block) %>%
    summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(vot_bSubj_partner_block, "output_stats/LEALCO-BEH_vot_betweenSubjects_partner_x_block.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-BEH_vot_betweenSubjects_partner_x_block_barplot.pdf")
c <- ggplot(vot_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
    labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
c
dev.off()
c

# plot (pointplot)
pdf("output_figures/LEALCO-BEH_vot_betweenSubjects_partner_x_block_pointplot.pdf")
tt <- ggplot(vot_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_point(data= vot_wSubj_partner_block, aes(y=mean, x=block, color=partner_type), stat="identity", position = position_jitterdodge(jitter.w = 0.05, dodge.width=(.9)), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

## LMM

Prepare the VOT data for LMMs. Note that we will be running he model on inverted naming latency (1/naming latency). This results in the magnitude of the datapoints being inverted. The estimates of the models have to be read accordingly.

```{r}

# select data
votINV <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot)

# Set sum contrasts for all variables.
votINV$partner_type <- droplevels(votINV$partner_type)
contrasts(votINV$partner_type) <- contr.sum(2)
contrasts(votINV$block)  <- contr.sum(2)

# check contrasts
contrasts(votINV$partner_type)
contrasts(votINV$block)

# center covariates
votINV <- votINV %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

votINV <- votINV %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

votINV <- votINV %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

votINV <- votINV %>%
  mutate(team = team - mean(team, na.rm=TRUE))

votINV$VOTinv_fact <- votINV$VOTinv * 10000

```

Try to find the maximally convergent model by using the *buildmer()* approach.

```{r}

# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- VOTinv_fact ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# select the maximal model that still converges
m_votINV <- buildmer(f,data=votINV,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_votINV)


sink("output_stats/LEALCO-BEH_votINV_lmm.txt")
print(summary(m_votINV))
sink()  # returns output to the console

save_model_to_html(m_votINV@model, 3, 'LEALCO-BEH_votINV_lmm.html')
```

Make model sanity checks. Everything seems ok.

```{r}
# qqplot
pdf("output_figures/LEALCO-BEH_votINV_lmm_qqplot.pdf")
qqnorm(residuals(m_votINV))
dev.off()

# histogram
pdf("output_figures/LEALCO-BEH_votINV_lmm_hist.pdf")
hist(residuals(m_votINV))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-BEH_votINV_lmm_residuals.pdf")
plot(residuals(m_votINV))
dev.off()
```

### Post-hoc / marginal means (Partner Type)

```{r}
# make post-hoc with no correction
m_votINV.emm_none_partner <-emmeans(m_votINV@model, pairwise ~ partner_type, adjust = "none")
m_votINV.ph_none_partner <- as.data.frame(m_votINV.emm_none_partner$contrasts)
write.csv(m_votINV.ph_none_partner,"output_stats/LEALCO-BEH_votINV_ph_none_partner.csv", row.names = FALSE)

# extract and save marginal means
m_votINV.mm_partner <- as.data.frame(m_votINV.emm_none_partner$emmeans)
m_votINV.mm_partner$emmean_untrans <- 1/m_votINV.mm_partner$emmean
m_votINV.mm_partner$lower.CL_untrans <- 1/m_votINV.mm_partner$upper.CL
m_votINV.mm_partner$upper.CL_untrans <- 1/m_votINV.mm_partner$lower.CL
write.csv(m_votINV.mm_partner,"output_stats/LEALCO-BEH_votINV_lmm_marginal_partner.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-BEH_votINV_lmm_marginal_partner_pointplot.pdf")
tt <- ggplot(m_votINV.mm_partner, aes(y=emmean_untrans, x=partner_type, color=partner_type)) + 
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### Post-hoc / marginal means (Block)

```{r}

# make post-hoc with no correction
m_votINV.emm_none_block <-emmeans(m_votINV@model, pairwise ~ block, adjust = "none")
m_votINV.ph_none_block <- as.data.frame(m_votINV.emm_none_block$contrasts)
write.csv(m_votINV.ph_none_block,"output_stats/LEALCO-BEH_votINV_ph_none_block.csv", row.names = FALSE)

# extract and save marginal means
m_votINV.mm_block <- as.data.frame(m_votINV.emm_none_block$emmeans)
m_votINV.mm_block$emmean_untrans <- 1/m_votINV.mm_block$emmean
m_votINV.mm_block$lower.CL_untrans <- 1/m_votINV.mm_block$upper.CL
m_votINV.mm_block$upper.CL_untrans <- 1/m_votINV.mm_block$lower.CL
write.csv(m_votINV.mm_block,"output_stats/LEALCO-BEH_votINV_lmm_marginal_block.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-BEH_votINV_lmm_marginal_block_pointplot.pdf")
tt <- ggplot(m_votINV.mm_block, aes(y=emmean_untrans, x=block)) + 
  #scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### Post-hoc / marginal means for (Partner Type x Block)

Compute post-hoc tests and export.

```{r}
# make post-hoc with tukey correction
m_votINV.emm_tukey_partner_x_block <-emmeans(m_votINV@model, pairwise ~ partner_type * block, adjust = "tukey")
m_votINV.ph_tukey_partner_x_block <- as.data.frame(m_votINV.emm_tukey_partner_x_block$contrasts)
write.csv(m_votINV.ph_tukey_partner_x_block,"output_stats/LEALCO-BEH_votINV_ph_tukey_partner_x_block.csv", row.names = FALSE)

# make post-hoc with no correction
m_votINV.emm_none_partner_x_block <-emmeans(m_votINV@model, pairwise ~ partner_type * block, adjust = "none")
m_votINV.ph_none_partner_x_block <- as.data.frame(m_votINV.emm_none_partner_x_block$contrasts)
m_votINV.ph_none_partner_x_block$p.valueBonf2 = m_votINV.ph_none_partner_x_block$p.value *2
write.csv(m_votINV.ph_none_partner_x_block,"output_stats/LEALCO-BEH_votINV_ph_none_partner_x_block.csv", row.names = FALSE)

# extract and save marginal means
m_votINV.mm_partner_x_block <- as.data.frame(m_votINV.emm_tukey_partner_x_block$emmeans)
m_votINV.mm_partner_x_block$emmean_untrans <- 1/m_votINV.mm_partner_x_block$emmean
m_votINV.mm_partner_x_block$lower.CL_untrans <- 1/m_votINV.mm_partner_x_block$upper.CL
m_votINV.mm_partner_x_block$upper.CL_untrans <- 1/m_votINV.mm_partner_x_block$lower.CL
write.csv(m_votINV.mm_partner_x_block,"output_stats/LEALCO-BEH_votINV_lmm_marginal_partner_x_block.csv", row.names = FALSE)

# plot
tt <- ggplot(m_votINV.mm_partner_x_block, aes(y=emmean_untrans, x=block, color=partner_type)) + 
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming Latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1710)
tt
ggsave("output_figures/LEALCO-BEH_votINV_lmm_marginal_partner_x_block_pointplot.pdf", width=4 , height=3.5)
tt

```

# == Entrainment analysis ==

The following analysis examines the reaction between Label Maintenance and (inverted) Naming Latency. This is interesting because there could be a speed accuracy trade-off (i.e. entraining with the partner is cognitively costly) or on the contrary it is possible that entraining with the partner is in fact facilitatory.

```{r}
# aggregte accuracy (within subject)
acc_wSubj_partner <- data_trained %>%
  filter(!subjID %in%  exclusion_acc) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean_ACC = mean(correct), sd_ACC=sd(correct), sem_ACC=(sd(correct)/sqrt((length(correct)))), n_ACC=length(correct))

# aggregate VOTinv (within subjects) only for correct trials
votINV_wSubj_partner <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean_VOTinv = mean(VOTinv), sd_VOTinv=sd(VOTinv), sem_VOTinv=(sd(VOTinv)/sqrt((length(VOTinv)))), n_VOTinv=length(VOTinv))

# merge the two DVs in one dataframe
entrainment_data <- merge(acc_wSubj_partner,votINV_wSubj_partner,by=c("subjID","partner_type"))

# pivot from long to wide
entrainment_data <- entrainment_data %>% 
  pivot_wider(
    names_from = partner_type, 
    values_from = c(mean_ACC, sd_ACC, sem_ACC, n_ACC, mean_VOTinv, sd_VOTinv, sem_VOTinv, n_VOTinv)
  )

# calculate entrainment scores (same - different)
entrainment_data$entrainment_ACC <- entrainment_data$mean_ACC_same - entrainment_data$mean_ACC_different
entrainment_data$entrainment_VOTinv <- (entrainment_data$mean_VOTinv_same - entrainment_data$mean_VOTinv_different) * 10000

# correlation
corr <- cor.test(entrainment_data$entrainment_ACC, entrainment_data$entrainment_VOTinv)
sink('output_stats/LEALCO-BEH_entrainment_correlation_invVOT.txt')
print(corr)
sink()

# format for plot
if (corr$p.value < 0.001) {
  txt <- paste0('R=', round(corr$estimate, digits = 3), "\np<0.001")
} else {
  txt <- paste0('R=', round(corr$estimate, digits = 3), "\np=", round(corr$p.value, digits = 3) )
}

# scatterplot
s <- ggplot(entrainment_data, aes(x=entrainment_VOTinv, y=entrainment_ACC)) +
  geom_point() +
  stat_smooth(method=lm, fullrange=TRUE, color = 'black') + 
  geom_hline(yintercept=0, linetype="dotted") +
  geom_vline(xintercept=0, linetype="dotted") +
  xlim(-2.5, 2.5) +
  ylim(-0.5, 0.5) +
  geom_text(x=1.5, y=-0.4, label=txt) +
  #xlab('<- faster for different                                                              faster for same ->\n\nSpeed advantage\n(same - different)') +
  xlab('Partner-Specific Naming Latency\n(same vs. different)') +
  ylab('Partner-Specific Label Maintenance\n(same vs. different)') +
    theme(axis.text=element_text(size=12), axis.title=element_text(size=12))
ggsave("output_figures/LEALCO-BEH_entrainment_correlation_invVOT.pdf", width=6, height=3.5)
s

```

```{r}
# Plot the correlation
p3<- ggplot(entrainment_data, aes(x=mean_VOTinv_same, y=mean_ACC_same)) +
     geom_point(color=pal1[1]) +
     geom_smooth(method=lm , color=pal1[1], se=FALSE) +
     geom_point(aes(x=mean_VOTinv_different, y=mean_ACC_different), color=pal1[2]) +
     geom_smooth(aes(x=mean_VOTinv_different, y=mean_ACC_different), method=lm , color=pal1[2], se=FALSE) +
     xlab('Naming Latencies (inverted)') +
     ylab('Label Maintenance') 
 p3
 ggsave("output_figures/LEALCO-BEH_correlation_behavioral_invVOT.pdf")
 
# make separate correlations for same and differet
cor_same <- cor.test(entrainment_data$mean_VOTinv_same, entrainment_data$mean_ACC_same)
cor_diff <- cor.test(entrainment_data$mean_VOTinv_different, entrainment_data$mean_ACC_different)
sink('output_stats/LEALCO-BEH_correlation_behavior_invVOT.txt')
print(cor_same)
print(cor_diff)
sink()
print(cor_same)
print(cor_diff)
```

# Session Information

```{r}
sessionInfo()
```
